### 2020-08-31 thesis/chap_1.tex
fix naming

In the subsequent description, we make the distinction between:
\begin{itemize}
\item{\textit{historic runs}}, parameterized to reproduce the changes that happened between 1990 and 2010 in the region, with a different set of transition targets for 1990-2000 and 2000-2010.
\item{\textit{forecast runs}}, parameterized to project forward an average of the trends observed in the two decades, with a single set of transition targets (average of the two 1990-2000 and 2000-2010 targets) and for which only certain set of spatial multipliers change depending on climatic scenarios.
\end{itemize}
We defined two land use change scenarios, crossed with two different climate change scenarios, plus a control climate scenario. Those six scenarios in total are designed to  encompass the realm of possible future habitat changes for our 5 focal species.
The two land use change scenarios are:
\begin{itemize}
\item{\textbf{Business As Usual (BAU)}}: the land use change trends are projected forward into the future with no alteration to those trends.
\item {\textbf{Business As Usual + Reforestation (BAU-R)}}: the land use change trends are projected forward into the future, and reforestation is randomly occurring, converting to forest as much land as is lost through urbanization, for every timestep.
\end{itemize}
The climate scenarios influence the probability of transitions between forest types (i.e. succession and disturbances) they subsequently influence habitat suitability and connectivity. The three climate scenarios are:
\begin{itemize}
\item{\textbf{Historic (HIST)}}: No forest change: forest remains as it was in 2010. This is equivalent to a control treatment.
\item{\textbf{Baseline (BASE)}}: Forest change continues as it does in today's climate.
\item{\textbf{RCP 8.5 (RCP8)}}: The forest changes according to the emissions scenario RCP 8.5, characterized by increasing green-house gas emissions, high rates of population growth, modest GDP growth and low rates of technological development and uptake. It is the most severe of the future scenarios \citep{ipcc_summary_2013}.\\
\end{itemize}

@@

The final list of scenarios is the following:
\begin{itemize}
\item Historic run - 1990 to 2010 \textbf{(HIST)}. In this historic run, the forest type for all three time steps was taken from the LANDIS inputs (forest type data 2010). This is of course not accurate, but because no change is allowed to take place, this is not a problem and it is only there to allow consistency and comparison with the other scenarios.
\item Forecast land use BAU - Historic climate - 2010 to 2100 \textbf{(BAU-HIST)}
\item Forecast land use BAU - Baseline climate - 2010 to 2100 \textbf{(BAU-BASE)}
\item Forecast land use BAU - RCP 8.5 climate - 2010 to 2100 \textbf{(BAU-RCP8)}
\item Forecast land use reforestation - Historic climate - 2010 to 2100 \textbf{(BAU-R-HIST)}
\item Forecast land use reforestation - Baseline climate - 2010 to 2100 \textbf{(BAU-R-BASE)}
\item Forecast land use reforestation - RCP 8.5 climate - 2010 to 2100 \textbf{(BAU-R-RCP8)}\\
\end{itemize}

>>>>

In the subsequent description, we make the distinction between:
\begin{itemize}
\item{\textit{historic runs}}, parameterized to reproduce the changes that happened between 1990 and 2010 in the region, with a different set of transition targets for 1990-2000 and 2000-2010.
\item{\textit{forecast runs}}, parameterized to project forward an average of the trends observed in the two decades, with a single set of transition targets (average of the two 1990-2000 and 2000-2010 targets) and for which only certain set of spatial multipliers change depending on climatic scenarios.
\end{itemize}
We defined two land use change scenarios, crossed with two different climate change scenarios, plus a control climate scenario. Those six scenarios in total are designed to  encompass the realm of possible future habitat changes for our 5 focal species.
The two land use change scenarios are:
\begin{itemize}
\item{\textbf{Business As Usual (BAU)}}: the land use change trends are projected forward into the future with no alteration to those trends.
\item {\textbf{Business As Usual + Reforestation (R)}}: the land use change trends are projected forward into the future, and reforestation is randomly occurring, converting to forest as much land as is lost through urbanization, for every timestep.
\end{itemize}
The climate scenarios influence the probability of transitions between forest types (i.e. succession and disturbances) they subsequently influence habitat suitability and connectivity. The three climate scenarios are:
\begin{itemize}
\item{\textbf{Historic (Hist)}}: No forest change: forest remains as it was in 2010. This is equivalent to a control treatment.
\item{\textbf{Baseline (Base)}}: Forest change continues as it does in today's climate.
\item{\textbf{RCP 8.5 (RCP8)}}: The forest changes according to the emissions scenario RCP 8.5, characterized by increasing green-house gas emissions, high rates of population growth, modest GDP growth and low rates of technological development and uptake. It is the most severe of the future scenarios \citep{ipcc_summary_2013}.\\
\end{itemize}

@@

The final list of scenarios is the following:
\begin{itemize}
\item Historic run - 1990 to 2010 \textbf{(Hist)}. In this historic run, the forest type for all three time steps was taken from the LANDIS inputs (forest type data 2010). This is of course not accurate, but because no change is allowed to take place, this is not a problem and it is only there to allow consistency and comparison with the other scenarios.
\item Forecast land use BAU - Historic climate - 2010 to 2100 \textbf{(BAU-Hist)}
\item Forecast land use BAU - Baseline climate - 2010 to 2100 \textbf{(BAU-Base)}
\item Forecast land use BAU - RCP 8.5 climate - 2010 to 2100 \textbf{(BAU-RCP8)}
\item Forecast land use reforestation - Historic climate - 2010 to 2100 \textbf{(R-Hist)}
\item Forecast land use reforestation - Baseline climate - 2010 to 2100 \textbf{(R-Base)}
\item Forecast land use reforestation - RCP 8.5 climate - 2010 to 2100 \textbf{(R-RCP8)}\\
\end{itemize}
